\chapter{Fields}

\section{Extenstion Fields}

\subsection{Simple Extension}

\begin{definition}[Field Extension]
    Let $F$ be a field. A \bred{field extension} $K$ of $F$ is a field 
    that contains $F$ as subfield. We denote this by $K/F$ or $K : F$. 
    The degree of the extension $K$ over $F$ is denoted $[K : F]$ or $\dim_F K$, and is
    defined as the dimension of $K$ as a vector space over $F$.
\end{definition}

\begin{definition}
    Let $E$ be an extension field of a field $F$ and let $\mathfrak{a} \in E$. We call an element 
    $\mathfrak{a}$ \bred{algebraic} over $F$ if $\mathfrak{a}$ is the zero of some nonzero 
    polynomial in $F[x]$. If $\mathfrak{a}$ is not algebraic over $F$, it is called 
    \bred{transcendental} over $F$.
\end{definition}

\begin{example}
    $\mathbb{C}$ is an extension field of $\mathbb{R}$.
    \[
        \begin{tikzcd}[row sep=1.0em]
            \mathbb{C} \arrow[dash]{d}\\
            \mathbb{R}
        \end{tikzcd}
    \]
    The imaginary number $i = \sqrt{-1}$ is said to be algebraic since $x^2 + 1 = 0 \in \mathbb{R}[x]$. While 
    $\pi$ is transcendental since it is not a zero in $\mathbb{R}[x]$.
\end{example}

\begin{theorem}
    Let $K$ be an extension field of $F$, and $u \in K$ is an algebraic element over $F$. Then there exists 
    a unique monic irreducible polynomial $p(x)$ in $F[x]$ that has $u$ as a root. 
    Furthermore if $u$ is a root of $g(x) \in F[x]$, then $p(x)$ divide $g(x)$.
\end{theorem}
\begin{proof}
    Notice that $u \in K$ is algebraic over $F$ if and only if there is a nonzero polynomial 
    $f(x) \in F[x]$ such that $f(u) = 0_K$.

    Let $S$ be the set of all nonzero polynomials in $F[x]$ that have $u$ as a root, then $S$ is nonempty set.
    By well-ordering principle, $\exists p(x) \in S$ such that $p(x)$ has the smallest degree in $S$.

    Suppose that $f(x) \in F[x]$ with $f(u) = 0_K$. By division algorithm, 
    \[
        f(x) = p(x) q(x) + r(x)
    \]
    with $\deg p(x) > \deg r(x)$ or $r(x) = 0$.

    If $r(x) \neq 0$, 
    \[
        f(x) - p(x) q(x) = r(x) \> \Longrightarrow f(u) - p(u) q(u) = r(u) = 0.
    \]
    This contradicting the fact that $p(x)$ is the smallest polynomial. Thus $r(x) = 0$ and 
    $p(x)$ divide $f(x)$. And now if we let $p(x)$ and $q(x)$ be the smallest polynomial. Then, 
    $p(x) | q(x)$ and $q(x) | p(x)$ implies that $p(x) = q(x)$.
\end{proof}

\begin{remark}
    The $p(x)$ is called the "minimal polynomial of $u$ over $F$".
\end{remark}

\begin{theorem}[Minimal polynomial]
    Suppose $E$ is a field extension of $F$, and $\alpha \in E$ is algebraic over $F$. 
    Suppose the degree of the minimal polynomial $m_{\alpha}(x)$ of 
    $\alpha$ over $F$ is $n$. Then every element of $F(\alpha)$ can be written uniquely in the form 
    \begin{equation}
        c_0 + c_1 \alpha + c_2 \alpha^2 + \cdots + c_{n-1} \alpha^{n-1}
    \end{equation}
    for some $\alpha_i$'s in $F$
\end{theorem}
\begin{proof}
    By the first isomorphism theorem of rings, we said that 
    \[
        \overline{\phi}_\alpha : F[x] / \langle m_\alpha(x) \rangle \to F[\alpha], 
        \quad \overline{\phi}_\alpha(f(x) + \langle m_\alpha(x) \rangle) := f(\alpha)
    \]
    is an isomorphism. Every element of $F[x] / \langle m_\alpha(x) \rangle$ can be 
    uniquely written as $(\sum^{n-1}_{i=0} c_ix^i) + \langle m_\alpha(x) \rangle$ 
    for some $c_i$'s in $F$. Hence, we obtain the conclusion that 
    every element of $F[\alpha]$ can be uniquely written as 
    \[
        \overline{\phi}_\alpha \left( \sum^{n-1}_{i=0} c_ix^i + \langle m_\alpha(x) \rangle \right) = \sum^{n-1}_{i =0} c_i \alpha^i.
    \]
    This completes the proof.
\end{proof}

\begin{example}
    $\mathbb{R}$ is an extension field of $\mathbb{Q}$ and $\sqrt{3} \in \mathbb{R}$ is algebraic,
    then
    \[
        p(x) = x^2 - 3 \in \mathbb{Q}[x]
    \]
\end{example}

\begin{example}
    $\mathbb{R}$ is an extension field of $\mathbb{Q}$ and $\sqrt{3} + \sqrt{5} \in \mathbb{R}$ is algebraic,
    Then
    \[
        p(x) = x^4 - 16x^2 + 4 \in \mathbb{Q}[x].
    \]
\end{example}
\begin{solution}
    Let $x = \sqrt{3} + \sqrt{5} \in \mathbb{R}$, then 
    \begin{align*}
        x^2 = 3 + 2\sqrt{15} + 5 &\Rightarrow x^2 - 8 = 2\sqrt{15}\\
        &\Rightarrow (x^2 - 8)^2 = 4 \cdot 15\\
        &\Rightarrow x^4 - 16x^2 + 4 = 0
    \end{align*}
    Thus $p(x) = x^4 - 16x^2 + 4 \in \mathbb{Q}[x]$.
\end{solution}

\begin{theorem}
    Let $K$ be an extension field of $F$ and $u \in K$ is an algebraic element 
    over $F$ with minimal polynomial $p(x)$ of degree $n$, then 
    \begin{enumerate}
        \item $F[u]$ is a field isomorphism of $F[x]/p(x)$.
        \item $\{ 1, u, u^2, \ldots, u^{n-1}\}$ is a basis of the 
            vector space $F(u)$ over $F$.
        \item $[F(u):F]=n$.
    \end{enumerate}
\end{theorem}
\begin{proof}
    \begin{enumerate}
        \item Since $F(u)$ contains $F$ and $u$, so $F(u)$ contains every element of the form 
        \[
            b_0 + b_1u + b_2u^2 + \cdots + b_tu^t \quad \forall b_i \in F.
        \]
        We again define a function $\varphi : F[x] \to F(u)$ by 
        \[
            \varphi(f(x)) = f(u).
        \]
        Then $\varphi$ is ring homomorphism.

        Note that $ker\, \varphi = \langle p(x) \rangle$ where $p(x)$ is the minimal polynomial 
        of $u$ over $F$. By the first isomorphism theorem, $F[x] / p(x) \cong \Ima \varphi$.
        Since $p(x)$ is irreducible, the quotient ring $F[x] / \langle p(x) \rangle$ is a field and 
        $\Ima \varphi$ is also a field.

        Note that $\varphi(c) = c \> \forall c \in F$ and $\varphi (x) = u$. Thus $F \subset \Ima \varphi$ and 
        $u \in \Ima \varphi$. By definition of simple extension, $F(u) = \Ima \varphi$.

        \item Since $F(u) = \Ima \varphi, \> \forall w \in F(u), \exists f(x) \in F \> s.t. \>
        f(u) = w$. If $\deg f(x) > n$. By division algorithm, we have 
        \[
            f(x) = p(x) q(x) + r(x)
        \]
        If $r(x) = 0$, $f(u) = p(u)q(u) = 0 = w$.

        Otherwise, if $r(x) \neq 0$, then 
        \[
            r(x) = f(x) - p(x)q(x) \Longrightarrow r(u) = f(u) - p(u)q(u) = w
        \]
        with $\deg r(x) < n$. Thus 
        \[
            F(u) = \text{Span}\{1 , u, u^2, \ldots, u^{n-1} \}.
        \]
        
        \item Let $c_0 +c_1u + c_2u^2 + \cdots + c_{n-1}u^{n-1} = 0$. If 
        $\exists c_k \in F \> s.t. \> c_k \neq 0$. Then $p(x)$ is not the minimal polynomial of 
        $u$ over $F$. Thus $c_i = 0 \forall c_i \in F$. Hence, we can say that 
        $\{1, u, u^2, \ldots, u^{n-1} \}$ is linearly independent and it is also 
        a basis of $F(u)$ over $F \Longrightarrow |F(u):F| = n$.
    \end{enumerate}
\end{proof}

\begin{example}
    $\mathbb{Q}[\sqrt{3}]$ is isomorphic to $\mathbb{Q}[\sqrt{3}]/\langle x^2 - 3 \rangle$
\end{example}

\begin{example}
    If $u$ and $v$ have the same minimal polynomial $p(x)$ in $F[x]$, then $F(u)$ is 
    isomorphic to $F(v)$. For instance,
    \[
        \mathbb{Q}[\sqrt{3}] \cong \mathbb{Q}[-\sqrt{3}].
    \]
\end{example}

Let $\sigma: F \to E$ be an isomorphism then we again define 
$\olsi{\sigma} : F[x] \to E[x]$ by for $a_0 + a_1x + \cdots + a_n x^n \in F[x]$. We can write 
\begin{equation}
    \sigma (a_0 + a_1x + \cdots + a_n x^n) = \sigma(a_0) + \sigma(a_1x) + \cdots + \sigma(a_n x^n)
\end{equation}
and $\olsi{\sigma}$ is also isomorphism.

\begin{corollary}
    Let $\sigma : F \to E$ be an isomorphism of fields. Let $u$ be an algebraic element in 
    "some" extension field of $F$ with minimal polynomial $p(x) \in F[x]$. Again we let 
    $v$ be an algebraic element in some extension field of $E$ with minimal polynomial 
    $\sigma p(x) \in E[x]$. Then $\sigma$ extends to an isomorphism of fields 
    $\olsi{\sigma} : F(u) \to E(v)$ such that 
    \[
        \olsi{\sigma}(u) = v \> \text{ and } \> \olsi{\sigma}(c) = \sigma(c) \quad \forall c \in F.
    \]
\end{corollary}
\begin{proof}
    By previous theorem, $\varphi:F[x]/\left( p(x) \right) \to F(u)$ and
    $\olsi{\varphi}:E[x]/\left( \sigma p(x) \right) \to E(v)$ are isomorphism where 
    $\varphi( \left[ f(x) \right]) = f(u)$ and $\olsi{\varphi}( \left[ g(x) \right]) = g(v)$.

    Furthermore, we let $\xi $ be the surjective isomorphism
    \[
        \olsi{\xi}: E[x] \to E[x]/(\sigma p(x))
    \]
    defined by $\olsi{\xi}(g(x)) = |g(x)|$.
    
    Note that
    \[
        \begin{tikzcd}[row sep=2.5em]
            F[x] \arrow[r, "\sigma"] \arrow[dash]{d} & E[x] \arrow[r, "\olsi{\xi}"] \arrow[dash]{d} & E[x] / \left( \sigma p(x)\right) \arrow[r, "\olsi{\varphi}"] \arrow[dash]{d}& E[v] \arrow[dash]{d}\\
            f(x) \arrow[r] & \sigma f(x) \arrow[r] &  \left[ \sigma f(x) \right] \arrow[r] & \sigma f(v)\\
        \end{tikzcd}
    \]
    Since $\sigma, \olsi{\varphi}$ and $\olsi{xi}$ are surjective, so is the composite function.
    \begin{align*}
        ker\, \olsi{\phi}(\olsi{\xi}(\sigma)) &= 
        \{ f(x) \in F[x] \> | \> \sigma f(v) = 0 \}\\
        &= \{ f(x) \in F[x] \> | \> \sigma f(x) \in \langle \sigma f(x) \rangle \}\\
        &= \langle p(x) \rangle
    \end{align*}
    By First isomorphism theorem,
    \[
        F(u) \cong F[x] / \langle p(x) \rangle \cong^{\theta} E(v)
    \]
    Since $\theta([f(x)]) = \sigma f(v)$. Note that 
    \[
        \theta([x]) = \sigma \cdot 1_F \cdot v = 1_V \cdot v = v
    \]

    so we have the following situation
    \[
        \begin{tikzcd}[row sep=1.0em]
            F(u) & F[x] / \langle p(x) \rangle \arrow[l, "\varphi"] \arrow[r, "\theta"] & E(v)\\
            f(u) & \left[ f(x) \right] \arrow[l, "\varphi"] \arrow[r, "\theta"] & \sigma f(v)\\
            c & \left[ c \right] \arrow[l, "\varphi"] \arrow[r, "\theta"] & \sigma(c)\\
        \end{tikzcd}
    \]

    The composite function $\theta \circ \varphi^{-1} : F(u) \to E(v)$ is an isomorphism 
    that extends $\sigma$ and maps $u$ to $v$. 
    \[
        \tikz[overlay]{
      \draw (8.5,-2.25) node[anchor=south, color=cyan!70!black] {\textsf{By First isomorphism thm.}};
      \draw[ultra thick, cyan!70!black, fill=cyan!90!black, opacity=0.25, rounded corners] (5.35,-1.65) --
      (10,-1.65) --  (10,0.01) --  (7.35,0.01) --  (7.35,1.225) -- (2.82,1.225) -- (2.82,0.02) -- (5.35,0.02) -- cycle;
        }
        \begin{tikzcd}[row sep=2.5em]
            & F \arrow[r, "\sigma"] \arrow[dash, "\subseteq"]{d} & E \arrow[dash, "\subseteq"]{d} & \\
            & F[x] \arrow[r, "\sigma"] \arrow[d, "\xi"] & E[x] \arrow[d, "\olsi{\xi}"] & \\  
            F(u) \arrow[r, "\varphi"] & F[x] / \langle p(x) \rangle \arrow[r, "\sigma"] & E[x] / \langle \sigma p(x)\rangle \arrow[r, "\olsi{\varphi}"] & E(v)\\
        \end{tikzcd}
    \]
\end{proof}

\begin{example}
    $x^3 - 2$ is irreducible in $\mathbb{Q}[x]$ by Eisenstein's criterion. $\sqrt[3]{2} \in \mathbb{R}$ is a root of it.
    Verify that $\sqrt[3]{2} \omega$ is also a root of $x^3 - 2$ in $\mathbb{C}$ where 
    \[
        \omega = \frac{-1 + \sqrt{3}i}{2}
    \]
    is a complex cube root of $1$.
\end{example}
\begin{solution}
    Let $\sigma$ be the identity function from $\mathbb{Q}$ to $\mathbb{Q}$. By applying the previous corollary, we have
    \[
        \mathbb{Q}(\sqrt[3]{2}) \cong^\theta \mathbb{Q}(\sqrt[3]{2} \omega) 
    \]
    such that $\olsi{\sigma}(\sqrt[3]{2}) = \sqrt[3]{2} \omega$. And now $(\sqrt[3]{2} \omega)^3 = 2 \omega^3 = 2$.
\end{solution}


\subsection{Algebraic Extension}

\begin{definition}[Algebraic extension]
    An extension field $K$ of a field $F$ is said to be an algebraic extension of $F$ if every element 
    of $K$ is algebraic over $F$. 
\end{definition}

\begin{example}
    $\mathbb{C}$ is an algebraic extension of $\mathbb{R}$. $\forall a+bi \in \mathbb{C}$, where 
    $a,b \in \mathbb{R}$ and $i = \sqrt{-1}$. We have 
    \[
        (x+a+bi)(x+a-bi) = x^2 +2ax + a^2 + b^2.
    \]
    Thus $a+bi$ is a root of $x^2 +2ax + a^2 + b^2 = 0$.
\end{example}

\begin{theorem}
    If $K$ is a finite-dimensional extension field of $F$, then $K$ is an algebraic extension of $F$.
\end{theorem}
\begin{proof}
    Let $\{ V_1, V_2, \ldots, V_n \}$ be the basis of $K$ over $F$. For all $u \in K$, 
    $\{ 1, u, u^2, \ldots, u^n \}$ is linearly dependent. That is, 
    \[
        \exists u^k \in K \> s.t. \> u^k = \text{Span} \{1, u, u^2, \ldots, u^n\} = c_0 + c_1 u + c_2 u^2 +
        \cdots + c_{k-1} u^{k-1} (k \geq 1).
    \]
    Thus $u$ is a root of $f(x) = x^k - c_{k-1} u^{k-1} - \cdots - c_0$, this implies $K$ is an algebraic extension.
\end{proof}

\hrule
\vspace{10pt}

In fact, a simple extension is an algebraic extension if $u$ is algebraic. If extension field $K$ contains a 
transcental element $u$, then $K$ must be infinite dimensional over $F$.
\[
    \textsf{Non algebraic} \Longrightarrow \textsf{Infinite dimension}
\]
Note that $F(u)$ denote the intersection of all subfields of $K$ that contains both $F$ and $u$. It said to be a simple 
extension of $F$. If $u_1, u_2, \ldots, u_n$ are elements of an extension field $K$ of $F$. Let 
$F(u_1, \ldots, u_n)$ denote the intersection of all the subfields of $K$ that contain $F$ and every $u$ (known as 
generalized simple extension); $F(u, u_1, \ldots, u_n)$ is said to be a finitely generated extension of $F$.

\begin{theorem}
    If $K = F(u_1, u_2, \ldots, u_n)$ is a finitely generated extension field of 
    $F$ and each $u_i$ is algebraic over $F$, then $K$ is a finite-dimensional algebraic extension of $F$.
\end{theorem}
\begin{proof}
    Note that if $u, v$ is algebraic over $F$, then $v$ is algebraic over $F(u)$. Thus
    \[
        |F(u,v) : F(u)|\cdot |F(u) : F| < \infty \Longrightarrow 
        |F(u,v) : F| = |F(u,v) : F(u)| \cdot |F(u) : F| < \infty.
    \]
    By mathematical induction, we have 
    \[
        |F(u_1, u_2, \ldots, u_n) : F(u_1, u_2, \ldots, u_{n-1})| \ldots 
        |F(u_1) : F| < \infty
    \]
    which is also finite.
\end{proof}

\begin{corollary}
    If $L$ is algebraic extension of $K$ and $K$ is an algebraic extension of $L$. Then 
    $L$ is an algebraic extension field of $F$.
\end{corollary}
\begin{proof}
    $\forall \omega \in L, \> \exists f(x) \in K[x] \quad s.t. \> f(\omega) = a_0 + a_1 \omega 
    + \cdots + a_n \omega^n$. 

    Note that $F(a_0, a_1, \ldots, a_n)$ is finitely generated extension of $F$ and all $a_i$'s
    \\are algebraic. Thus it is finite dimensional algebraic extension of $F$. Since 
    $\omega$ is algebraic over $F(a_0, a_1, \ldots, a_n)$. So $F(a_0, a_1, \ldots, a_n)$ is finite 
    dimensional extension of $F \Longrightarrow \omega$ is algebraic over $F$.
    Thus $L$ is an algebraic extension of $F$.
\end{proof}

\begin{remark}
    Algebraic subfield $E$ of $\mathbb{C}$ over $\mathbb{Q}$ is called the \textbf{field of algebraic numbers}. 
    Where $E$ is an finite-dimensional algebraic extension over $K$.
    \[
        \begin{tikzcd}[row sep=tiny]
            \mathbb{C} &\\
             & E  \arrow[dash]{ul}
            \\
            \mathbb{Q} \arrow[uu, "\pi"] \arrow[ur, "\mu"]&\\
        \end{tikzcd}
    \]

    \begin{itemize}
        \item $\mu$ denote algebraic extension over $\mathbb{Q}$, e.g.: $\sqrt{2}, \sqrt{3}, i, \ldots$.
        \item $\pi$ denote non-algebraic extension.
    \end{itemize}
\end{remark}

\begin{corollary}
    Let $K$ be an extension field of $F$ and let $E$ be the set of all elements of $K$ that are 
    algebraic over $F$. Then $E$ is a subfield of $K$ and an algebraic extension field of $F$.
\end{corollary}
\begin{proof}
    We only need to show that $E$ is a field. Let $u,v \in F$, note that $F(u,v)$ 
    is finitely generated extension of $F$, so $E$ is algebraic extension.
    $E$ is closed under subtraction and multiplication. Moreover $u^{-1}$ is 
    algebraic over $F$. Thus $E$ is a subfield of $K$.
\end{proof}


\begin{example}
    \[
        \mathbb{Q}(i, -i) = \mathbb{Q}(i)
    \]
\end{example}

\begin{example}
    $$\mathbb{Q}(\sqrt{3}, i) = \mathbb{Q}(\sqrt{3})(i)$$
\end{example}
\begin{solution}
    \begin{align*}
        |\mathbb{Q}(\sqrt{3}, i)| &= |\mathbb{Q}(\sqrt{3})(i): \mathbb{Q}|\\
        &= |\mathbb{Q}(\sqrt{3})(i): \mathbb{Q}(\sqrt{3})| \, \cdot |\mathbb{Q}(\sqrt{3}): \mathbb{Q}|\\
        &= 2 \cdot 2\\
        &= 4
    \end{align*}
\end{solution}

\begin{example}
    Every finite-dimensional extension is also finitely generated. If $\{ u_1, u_2, \ldots, u_n \}$ 
    is a basis of $K$ over $F$. This implies $F(u_1, u_2, \ldots, u_n) \subseteq K$ and 
    $K \subseteq F(u_1, u_2, \ldots, u_n)$. 
    Thus,
    \[
        K = F(u_1, u_2, \ldots, u_n) = \text{Span}\{ u_1, u_2, \ldots, u_n \}.
    \]
\end{example}

\begin{example}[Non-example]
     $$\mathbb{Q}(\sqrt{3}, \sqrt{5}) \neq \mathbb{Q}(\sqrt{3})$$
\end{example}
\begin{solution}
    For the sake of contradiction, consider $\mathbb{Q}(\sqrt{3}, \sqrt{5}) = \mathbb{Q}(\sqrt{3})$, then 
    \[
        \sqrt{5} = a+ b\sqrt{3}, \quad \forall a,b \in \mathbb{Q}
    \]
    Altering this equation by moving $a$ to left-hand side, then squaring both sides. We obtain
    \begin{align*}
        (\sqrt{5} - a)^2 = (b\sqrt{3})^2 \quad &\Rightarrow 5 - 2\sqrt{5}a + a^2 = 3b^2\\
        &\Rightarrow \frac{5 + a^2 - 3b^2}{2a} = \sqrt{5} \quad (a\neq 0)
    \end{align*}
    However, when $a=0$, we have $5 = 3b^2$. Which is a contradiction.
\end{solution}

\section{Splitting Field}

In last chapter we had discussed about the integral domain. Suppose 
polynomial $f(x)$ has degree $n$. Then $f(x)$ has at most $n$ roots in \textit{any} field. 
Suppose that $K$ contains fewer than $n$ roots of $f(x)$. It might be possible to find an extension field of 
$K$ that contains additional roots of $f(x)$. 

\begin{definition}[Splitting field]
    If $F$ is a field and $f(x) \in F[x]$, then an extension field $K$ of $F$ is said to 
    be a \bred{splitting field} (or \bred{root field}) of $f(x)$ over $F$ provided that 
    \begin{itemize}
        \item $f(x)$ splits over $K$, say 
        \begin{equation}
            f(x) = c(x-u_1)\ldots (x-u_n)
        \end{equation}
        \item and
        \begin{equation}
            K = \underbrace{F(u_1, u_2, \ldots, u_n).}_{\text{smallest field}}
        \end{equation}
    \end{itemize}
\end{definition}

\begin{example}
    If $f(x) = x^4 - x^2 - 2 = (x^2 - 2)(x^2 + 1)$ in $\mathbb{Q}[x]$. Then 
    \[
        \mathbb{Q}(\sqrt{2}, -\sqrt{2}, i, -i) = \mathbb{Q}(\sqrt{2}, i)
    \]
    is a splitting field of $f(x)$ over $\mathbb{Q}$.
\end{example}

\subsection{Separability}

\begin{definition}[Separable polynomial]
    Let $K$ to be a field. A nonzero polynomial $f(x) \in K[x]$ is 
    \textit{separable} when it has distinct roots in a splitting field 
    over $K$. That is, each root of $f(x)$ can only be appears one at the time. 
    If $f(x)$ has multiple root then $f(x)$ is called \textit{inseparable}.
\end{definition}

\begin{example}
    In $\mathbb{R}[x]$, the polynomial $f(x) = x^2 - x$ is separable since it has two distinct roots: 
    $0$ and $1$. And $x^3 - 2$ is separable since there are three distinct roots: $\sqrt[3]{2}, \sqrt[3]{2} \omega, \sqrt[3]{2} \omega^2$ 
    in the complex plane.
\end{example}

\begin{example}
    In $\mathbb{F}_3[x]$ the polynomial $f(x) = x^3 - 1 = (x-1)^3 = (x+1)^3$ is inseparable since it has a multiple root $1$. 
\end{example}

\begin{theorem}
    A nonzero polynomial $f(x) \in K[x]$ is separable if and only if it is relatively prime to its derivative $f'(x)$ 
    in $K[x]$.
\end{theorem}
\begin{proof}
    Let $f(x)$ be a nonzero polynomial in $K[x]$. 
    
    $(\Rightarrow)$ Suppose that $f(x)$ is separable and let
    $\alpha$ be a root of $f(x)$ in some extension field of $K$. Then
    \[
        f(x) = (x - \alpha) g(x), \quad \text{with } g(\alpha) \neq 0.
    \]
    Since $f'(\alpha) = g(\alpha) \neq 0$, so $\alpha$ is not a root of $f'(x)$. Thus $f(x)$ and $f'(x)$ have no common roots, 
    and hence they have no common factor in $K[x]$ --- they are relatively prime.
    
    $(\Leftarrow)$ If $f(x)$ is not separable, so by definition it has a repeated root $\alpha$ in some extension field of $K$. 
    This root is also a root $f'(x)$. Thus $f(x) = (x - \alpha)^2 g(x)$ for some $g(x) \in K[x]$. By product rule, we have
    \[
        f'(x) = (x - \alpha)^2 g'(x) + 2(x - \alpha) g(x)
    \]
    So $f'(\alpha) = 0$ implies that $f(x)$ and $f'(x)$ have a common factor $(x - \alpha)$ in $K[x]$. In particular, 
    $f(x)$ and $f'(x)$ are not relatively prime (in $K[x]$). Taking the contrapositive, 
    if $f(x)$ and $f'(x)$ are relatively prime, then $f(x)$ is separable.
\end{proof}

\begin{example}
    In $\mathbb{F}_3[x]$, let $f(x) = x^6 + x^5 + x^4 + 2x^3 + 2x^2 +x + 2$. Using Euclid's algorithm to verify that $f(x)$ is inseparable.
\end{example}
\begin{solution}
    We first compute the derivative 
    \[
        f'(x) = 6x^5 + 5x^4 + 4x^3 + 6x^2 + 4x = 2x^4 + x^3 + x.
    \] 
    Then we apply Euclid's algorithm:
    \[
        f(x) = f'(x) \cdot (2x^2 + 2) + (2x^2 + 2)
    \]
    \[
        f'(x) = (2x^2 + 2) \cdot (x^2 + 2x + 2) + 0.
    \]
    The greatest common divisor is $2x^2 + 2 \neq 1$. Thus $f(x)$ is not separable in $\mathbb{F}_3[x]$.
\end{solution}

\begin{example}
    Let $f(x) = x^4 - 3x - 2$ in $\mathbb{Q}[x]$. Using Euclid's algorithm to verify that $f(x)$ is separable.
\end{example}
\begin{solution}
    We first compute $f'(x) = 4x^3 - 3$. Then we apply Euclid's algorithm to find 
    \[
        f(x) = f'(x) \cdot \left( \frac{1}{4}x \right) - \frac{9}{4}x - 2
    \]
    \[
        f'(x) = \left( - \frac{9}{4}x - 2 \right) \left(- \frac{16}{9}x^2 + \frac{128}{81}x - \frac{1024}{729}\right) \underbrace{- \frac{4235}{729}}_{\text{remainder}}.
    \]
    By inspection, we have reached a remainder that is a nonzero constant. Thus 
    $f(x)$ and $f'(x)$ are relatively prime in $\mathbb{Q}[x]$. Hence, $f(x)$ is separable.
\end{solution}

\section{Finite Fields}

\begin{theorem}
    Let $R$ be a ring with identity. Then 
    \begin{enumerate}
        \item The set 
        \[
            \mathfrak{G} = \{ k \cdot 1_R \> | \> k \in \mathbb{Z} \}
        \]
         is a subring of $R$.
        \item If $R$ has characteristic $0$, then $\mathfrak{G}$ is isomorphic to $\mathbb{Z}$.
        \item If $R$ has characteristic $n > 0$, then $\mathfrak{G}$ is isomorphic to $\mathbb{Z}_n$.
    \end{enumerate}
\end{theorem}
\begin{proof}
    We prove each of the statements listed above.
    \begin{enumerate}
        \item First of all, we use subring test to check if $\mathfrak{G}$ is a subring of $R$.
        \[
            \begin{cases}
                a \cdot 1_R - b \cdot 1_R = (a-b) \cdot 1_R \in \mathfrak{G}\\
                a \cdot 1_R \cdot b \cdot 1_R = ab\, 1_R \in \mathfrak{G}
            \end{cases}
        \]
        so $\mathfrak{G}$ is a subring of $R$. 
    \end{enumerate}

    We now prove (2), (3) at once, We consider a map $f : \mathbb{Z} \to \mathbb{R}$ 
    defined by 
    \[
        f(n) = n \cdot 1_R \quad \forall n \in \mathbb{Z}.
    \] 
    Then $f$ is homomorphism because 
    \[
        f(n + m) = (n + m) \cdot 1_R = f(n) + f(m)
    \]
    and the kernel is 
    \[
        ker\, f = \{ n \in \mathbb{Z} \> | \> n \cdot 1_R = 0_R \}.
    \]
    By the first isomorphism theorem, $\mathbb{Z} / ker\, f$ is isomorphic to $\mathbb{R}$.
    \begin{itemize}
        \item If $R$ has a characteristic $0$, then $ker\, f = \langle 0 \rangle \Longrightarrow \mathbb{Z} \cong \mathbb{R}$.
        \item If $R$ has a characteristic $n$, then $ker\, f = \langle n \rangle \Longrightarrow \mathbb{Z}/\langle n \rangle \cong \mathbb{R}$.
    \end{itemize}
\end{proof}

\begin{corollary}
    Every finite field has characteristic $p$ for some prime $p$.
\end{corollary}
\begin{proof}
    Since finite field is integral domain, it must has characteristic prime $p$.
\end{proof}

\begin{remark}
    \begin{enumerate}
        \item The converse of it is false. There are infinite fields of characteristic $p$ (i.e. $\mathbb{Z}_p[x]$). 
        \[
            \mathfrak{G} = \{ k \cdot 1_R \> | \> k \in \mathbb{Z} \}
        \]
        is called the prime subfield of $K$ and is contained in every subfield of $K$. Which means 
        every field of characteristic $p$ must contains $\mathbb{Z}_p$.

        \item The number of elements in a finite field $K$ is called the order of $K$.
    \end{enumerate}
\end{remark}

\subsection{Order of finite field}

\begin{theorem}
    A finite field $K$ has order $p^n$, where $p$ is the characteristic of $K$ 
    and $n = |K:\mathbb{Z}_p|$.
\end{theorem}
\begin{proof}
    Let $K$ be a finite dimensional extension of $\mathbb{Z}_p$. Let $n = |K:\mathbb{Z}_p|$, then 
    $\{ u_1, u_2, \ldots, u_n \}$ is a basis of $K$.

    $\forall k \in K$, $k$ is represented uniquely be 
    \[
        k = c_1 u_1 + c_2 u_2 + \cdots + c_nu_n.
    \]
    There are precisely $p^n$ distinct linear combinations of the form. Thus 
    $|K| = p^n$.
\end{proof}

\begin{lemma}[The Freshman's dream]
    Let $R$ be a commutative ring with identity of characteristic $p$, where $p$ is a prime.
    Then for every $a, b \in R$ and for all positive integer $n$ we have 
    \begin{equation}
        (a + b)^{p^n} = a^{p^n} + b^{p^n}.
    \end{equation}
\end{lemma}
\begin{proof}
    We will use the induction on $n$. 
    
    Assume $n = 1$, we expand $(a+b)^p$ with binomial theorem.
    \[
        (a+b)^p = \sum^p_{k=0} {p \choose k} a^{n-k}b^k = a^p + 
        {p \choose 1} a^{p-1}b + \cdots + {p \choose p-1} ab^{p-1} + b^p.
    \]
    Note that 
    \[
        {p \choose k} = \frac{p!}{(p-k)!\, k!}, \quad k, p-k < p \> \text{ for } 1 \leq k < p.
    \]
    This implies that $p$ divide ${p \choose k} \Longrightarrow 
    {p \choose k}a^{p-k}b^k = 0 \> (\text{mod } p)$. Thus $(a+b)^p = a^p + b^p$. 
    We are done for base case.

    Assume that it holds for all less than $n$.
    \begin{align*}
        (a+b)^{p^n} &= \left( (a+b)^p \right)^{p^{n-1}} \\
        &= (a^p + b^p)^{p^{n-1}}\\
        &= (a^p)^{p^{n-1}} + (b^p)^{p^{n-1}}\\
        &= a^{p^n} + b^{p^n}.
    \end{align*}

    Therefore the theorem is true for every positive integer $n$. Now we are done.
\end{proof}

\begin{theorem}[Existence of finite field]
    Let $K$ be an extension field $\mathbb{Z}_p$. For all positive integer $n$, 
    $K$ has order $p^n$ if and only if $K$ is a splitting field of $x^{p^n} - x$ over $\mathbb{Z}_p$.
\end{theorem}
\begin{proof}
    $(\Rightarrow)$ Let $f(x) = x^{p^n} - x$ over $\mathbb{Z}_p$. Then 
    \[
        f(x) = p^n x^{p^n - 1} - 1 = -1 
    \]
    and so $f(x)$ and $f'(x)$ are relatively prime $\Longrightarrow f(x)$ is separable.
    Then $f(x)$ has $p^n$ distinct roots in splitting field. Let $c$ be any nonzero 
    element of $K$. Let $\{c_1, c_2, \ldots, c_{p^n - 1}\}$ be all the nonzero elements of 
    $K$ and let 
    \[
        u = c_1 c_2 \cdots c_k.
    \]

    Note that $\{cc_1, cc_2, \ldots, cc_k\}$ are all distinct and nonzero elements of $K$. Thus 
    \[
        \{cc_1, cc_2, \ldots, cc_k\} = \{c_1, c_2, \ldots, c_{p^n - 1}\}
    \]
    and 
    \[
        cc_1 \cdot cc_2 \cdots cc_{p^n - 1} = c_1 \cdot c_2 \cdots c_{p^n - 1} \Rightarrow 
        c^{p^n - 1} = 1_K \Rightarrow c^{p^n} - c = 0.
    \]
    So all nonzero elements of $K$ consisting of the $p^n$ distinct roots of $x^{p^n} - x$ over 
    $\mathbb{Z}_p$.

    $(\Leftarrow)$ On the other hand, let $E$ be the subset of $K$ consisting of the 
    $p^n$ distinct roots of $x^{p^n} - x$. We want to show $E$ is a subfield of $K$. 

    For all $a,b$ in $E$, $a^{p^n} = a$ and $b^{p^n} = b$. So
    \[
        (a+b)^{p^n} = a^{p^n} + b^{p^n} = a+b \Rightarrow a+b\in E
    \]
    \[
        (ab)^{p^n} = a^{p^n}\, b^{p^n} = ab \Rightarrow ab\in E
    \]
    \[
        (-a)^{p^n} = (-1)^{p^n}\, a^{p^n} = -a \Rightarrow a\in E 
    \]
    and 
    \[
        (a^{-1})^{p^n} = (a^{p^n})^{-1} = a^{-1}.
    \]

    Clearly $0,1 \in E$. Since $K$ is a field, the rest of axioms are true. 
    Since $K$ is splitting field of $x^{p^n} - x, K \subseteq E$. Hence 
    $K = E$ and $|K| = |E| = p^n$.
\end{proof}

\section{Galois Theory}

The classical question of algebra : Whether or not there were formulas for the solution of higher degree polynomial 
equations. There are no formula for the solution of all polynomial equations of degree $n$ when $n \geq 5$.

Galois theory had a profound influence on the development of later mathematics for beyond the scope of 
the original solvability problem. Why? Because his theory connecting the field extensions with groups.

The \textit{Galois group} of an extension $E/F$, denoted $\gal_{F} E$, is the group 
of automorphisms of $E$ which are the identity on field $F$.

\begin{definition}[Galois group]
    Let $K$ be an extension field of $F$. An $F$-automorphism of $K$ is an isomorphism $\sigma : K \to K$ that 
    fixes $F$ elementwise. That is, $\sigma(c) \to c, \forall c \in F$.

    The set of all $F$-automorphisms of $K$ is denoted $\gal_F K$ and is called the Galois group of $K$ over $F$.
\end{definition}

\begin{remark}
    Some books use the notation $\gal(E/F)$ to denote the galois group of extension $E/F$. 
    In this notes we write $\gal_{F} E$, the subscript represents the field 
\end{remark}

\begin{theorem}
    If $K$ is an extension field of $F$, then $\gal_F K$ is a group under the operation 
    of composition of functions.
\end{theorem}
\begin{proof}
    We need to show that the function composition from a group:

    [Closedness]: $\forall \sigma, \tau \in \gal_F K, \quad \sigma \circ \tau (c) = c \> \forall c \in F$.
    
    [Associativity]: Associativity holds because of function composition's property.
    
    [Existence of identity]: $\forall \sigma \in \gal_F K$, $\sigma \circ \tau = \tau \circ \sigma = \sigma$.

    [Existence of inverse]: $\forall \sigma \in \gal_F K$, $\sigma^{-1}(c) = c \> \forall c \in F$. So 
    $\sigma^{-1}$ is the inverse in $\gal_F K$.
\end{proof}

\begin{theorem}
    Let $K$ be an extension field of $F$ and $f(x) \in F[x]$. If $u \in K$ is a root of $f(x)$ and $\sigma \in \gal_F K$, 
    then $\sigma(u)$ is also a root of $f(x)$.
\end{theorem}
\begin{proof}
    Take a $u \in K$, $f(u) = 0 \Longrightarrow \sigma(f(u)) = \sigma(0) = 0$. 

    Since $\sigma \in \gal_F K, \sigma \left( f(u) \right) = f\left( \sigma(u) \right) = 0$.
\end{proof}

\begin{remark}
    Every root of $p(x)$ in $K$ is the image of $u$ under some automorphism of $\gal_F K$.
\end{remark}

\begin{theorem}
    Let $K$ be the splitting field of some polynomial over $F$ and $u,v \in K$. Then there exists an $\sigma \in \gal_F K$ 
    such that $\sigma(u) = v$ if and only if $u$ and $v$ have the same minimal polynomial. 
\end{theorem}
\begin{proof}
    $(\Rightarrow)$ Note that if $K$ is splitting field of $f(x)$ with $\deg f = n$. Then 
    \[
        |K:F| \leq n! \Longrightarrow K \textsf{ is algebraic over } F.
    \]
    So $u$ has a minimal polynomial $q(x)$ over $F$.

    By previous theorem, $p(v) = 0$ and $q(u) = 0$. These imply $p(x) | q(x)$ and 
    $q(x) | p(x)$ and hence $p(x) = q(x)$. We are done for this direction.

    $(\Leftarrow)$ On the other hand, in simple extension, we can extend an isomorphism 
    $\sigma: F \to F$ to $\olsi{\sigma}: \olsi{F} \to \olsi{F}$ such that 
    $\olsi{\sigma}(u) = v$ and $\olsi{\sigma}(c) = c$ for all constant $c \in F$. 

    Since $K$ is splitting field of some polynomial over $F$, which is also a splitting field of 
    $F(u)$ and $F(v)$. We can extend an isomorphism $\olsi{\sigma}$ to an isomorphism 
    $\tilde{\sigma}: K \to K$. If $\sigma = 1$, then $\tilde{\sigma} \in \gal_F K$.
\end{proof}

\begin{example}
    Given that $\sigma \in \gal_\mathbb{R} \mathbb{C}$, find $\sigma(i)$.
\end{example}
\begin{solution}
    By previous theorem,
    \[
        \sigma(i) = \{ i, - i \}.
    \]
    Thus $\gal_F K = \{1, \sigma \}$ is a group of order 2 and hence $\gal_\mathbb{R} \mathbb{C}$ 
    is isomorphic to $\mathbb{Z}_2$.
\end{solution}

\begin{theorem}[Galois group of finitely generated extension]
    Let $K = F(u_1, u_2, \ldots, u_n)$ be an algebraic extension field of $F$. If 
    $\sigma \circ \tau \in \gal_F K $ and $\sigma(u_i) = \tau(u_i)$ for each $i = 1,2,\ldots, n$.
    Then $\sigma = \tau$.

    In other words, an automorphism in $\gal_F K$ is completely determined by its action 
    on $u_1, u_2, \ldots u_n$.
\end{theorem}
\begin{proof}
    Let $\beta = \sigma^{-1} \circ \tau$, then 
    \[
        \sigma^{-1} \circ \tau (u_i) = \sigma^{-1} \circ \sigma(u_i) = u_i.
    \]
    Let $v \in F(u_i)$, then there exists a constant $c_i \in F$ such that 
    \[
        c_0 + c_1u_1 + \cdots + c_{n-1}u^{n-1}_1 = w \Longrightarrow \beta(v) = v.
    \]
    Again we let $w \in F(u_1, u_2)$, then there exists a constant $c_i \in F$ such that 
    \[
        c_0 + c_1u_2 + \cdots + c_{n-1}u^{n-1}_2 = w \Longrightarrow \beta(w) = w.
    \]
    Repeating this process, we conclude that for all $v \in K$, $\beta(v) = v \Longrightarrow \beta = 1$.
    Thus $\tau = \sigma$.
\end{proof}

\begin{example}
    Consider $\sigma \in \gal_\mathbb{Q} \mathbb{Q}[\sqrt{3}, \sqrt{5}]$. We let two actions
    \[
        \tau(\sqrt{3}) = -\sqrt{3}, \quad \tau(\sqrt{5}) = \sqrt{5}
    \]
    and
    \[
        \alpha(\sqrt{3}) = \sqrt{3}, \quad \alpha(\sqrt{5}) = -\sqrt{5}
    \]
    and defined $\beta = \alpha \circ \tau$.

    Then $\gal_\mathbb{Q} \mathbb{Q}[\sqrt{3}, \sqrt{5}] = \{ 1, \tau, \alpha, \beta \}$
    such that

    \begin{center}
        \begin{tabular}{|c|c|c|c|c|}
            \hline
            & $1$ & $\tau$ & $\alpha$ & $\beta$\\
            \hline
            $\sqrt{3}$ & $\sqrt{3}$ & $-\sqrt{3}$ & $\sqrt{3}$ & $-\sqrt{3}$\\[0.225em]
            \hline
            $\sqrt{5}$ & $\sqrt{5}$ & $\sqrt{5}$ & $-\sqrt{5}$ & $-\sqrt{5}$\\
            \hline
        \end{tabular}
    \end{center}

    Note that $\tau, \alpha, \beta$ both have an order 2. Thus $\gal_\mathbb{Q} \mathbb{Q}[\sqrt{3}, \sqrt{5}] \cong 
    \mathbb{Z}_2 \times \mathbb{Z}_2$.
\end{example}

\begin{corollary}
    If $K$ is splitting field of a separable polynomial $f(x)$ of degree $n$ in $F[x]$, then $\gal_F K$ is isomorphic 
    to a subgroup of $S_n$.
\end{corollary}
\begin{proof}
    Let $u_1, u_2, \ldots, u_n$ be distinct roots of $f(x)$. Then $K = F(u_1, u_2, \ldots, u_n)$ and let 
    \[\mathcal{U} = \{ u_1, u_2, \ldots, u_n \}.\] For all permutation $\sigma \in \gal_F K$, $\forall 1 \leq i \leq n$, 
    $\sigma(u_i) = u_j$ for some $j$.

    Now define a function $\theta : \gal_F K \to S_n$ defined by $\theta: \sigma \mapsto \sigma \circ 1_\mathcal{U}$. $\theta$ 
    is well defined. Note that 
    \[
        \sigma \circ 1_\mathcal{U} = \tau \circ 1_\mathcal{U} \Longrightarrow \sigma = \tau
    \]
    by previous theorem. Thus $\theta$ is injective, and $\theta$ is homomorphism.

    By the first isomorphism theorem, we say that 
    \[
      \gal_F K \cong \Ima \theta = \textsf{a subgroup of } S_n.
    \]
\end{proof}

\subsection{Galois group of cubics}

\begin{theorem}[Galois group of cubics]
    Let $K$ to be a field with $\text{char} K \neq 2$, and $f(x)$ be a separable 
    irreducible cubic polynomial in $K[x]$. If the discriminant of $f$ is 
    a square in $K$ then the galois group of $f(x)$ over $K$ is $A_3$. 
    Otherwise, If the discriminant of $f$ is not
    a square in $K$, then the galois group of $f(x)$ over $K$ is $S_3$. 
\end{theorem}
\begin{proof}
    The permutation action of the Galois group of $f(X)$ on its roots turns the galois
group into a transitive subgroup of $S_3$. The only transitive subgroups of
$S_3$ are $A_3$ and $S_3$ itself, and we can decide when the galois group is in $A_3$ or not using the
discriminant.
\end{proof}

\section{Intermediate Fields}

\begin{definition}[Intermediate field]
    Let $K$ be an extension field of $F$. A field $E$ such that
    \[
        F \subseteq E \subseteq K
    \]
    is called an \bred{intermediate field} of the extension. Clearly 
    that $\gal_E K \cong \gal_F K$.
\end{definition}

\begin{theorem}
    Let $K$ be an extension field of $F$. If $H$ is a subgroup of $\gal_F K$, let 
    \[
        E_H = \{ k \in K \> | \> \sigma(k)=k \textsf{ for every } \sigma \in H \}.
    \]
    Then $E_H$ is an intermediate field of the extension $K$. The field $E_H$ is called 
    the "fixed field" of subgroup $H$.
\end{theorem}
\begin{proof}
    It is clear that $F \subseteq E_H \subseteq K$. So we only want to show that $E_H$ is a subfield.

    Let $a,b \in H$. For all $\sigma \in H$, we have 
    \[
        \sigma(a + b) = \sigma(a) + \sigma(b) = a+b
    \]
    \[
        \sigma(ab) = \sigma(a) \sigma(b) = ab
    \]
    \[
        \sigma(0_K) = 0_K, \sigma(1_K) = 1_K
    \]
    \[
        \sigma(-a) = - \sigma(a) = -a
    \]
    \[
        \sigma(a^{-1}) =\left( \sigma(a)\right)^{-1} = a^{-1}
    \]
    Thus $E_H$ is a subfield of $K$.
\end{proof}

\begin{example}
    From previous example,
    \[
        \mathbb{Q} \subseteq \mathbb{Q}[\sqrt{3}] \subseteq \mathbb{Q}[\sqrt{3}, \sqrt{5}].
    \]
    And $\gal_{\mathbb{Q}[\sqrt{3}]} \mathbb{Q}[\sqrt{3}, \sqrt{5}] = \{ 1, \alpha \}$, 
    and $\gal_{\mathbb{Q}} \mathbb{Q}[\sqrt{3}, \sqrt{5}] = \{1, \tau, \alpha, \beta \}$.
\end{example}

\begin{example}
    $\gal_{\mathbb{Q}[\sqrt{3}]} \mathbb{Q}[\sqrt{3}, \sqrt{5}] = \{ 1, \alpha \}$ is the fixed 
    field of $\mathbb{Q}[\sqrt{3}] = \{ 1, \alpha \}$, where 
    \[
        \alpha(\sqrt{3}) = \sqrt{3}, \alpha(\sqrt{5}) = -\sqrt{5}.
    \]
\end{example}
\begin{solution}
    For all $a_i \in \mathbb{Q}$. Compute
    \begin{align*}
        &\alpha (a_0 + a_1 \sqrt{3} + a_2 \sqrt{5} + a_3 \sqrt{15}) = a_0 + a_1 \sqrt{3} + a_2 \sqrt{5} + a_3 \sqrt{15}\\
        &\Longleftrightarrow \> a_0 + a_1 \sqrt{3} - a_2 \sqrt{5} - a_3 \sqrt{15} = a_0 + a_1 \sqrt{3} + a_2 \sqrt{5} + a_3 \sqrt{15}\\
        &\Longleftrightarrow \> a_2 \sqrt{5} + a_3 \sqrt{15} = 0\\
        &\Longleftrightarrow \> a_2 + a_3 \sqrt{3} = 0\\
    \end{align*}
    
    Since $a_2a^{-1}_3 \in \mathbb{Q} \Longrightarrow -\sqrt{3} \in \mathbb{Q}$, which is a contradiction. 
\end{solution}

\begin{example}
    $\gal_{\mathbb{R}} \mathbb{C} = \{ 1, \alpha \}$, and $\alpha(a + bi) \Longrightarrow a - bi = a+ bi \Longrightarrow b =0$. 
    Thus fixed field of $\gal_{\mathbb{R}} \mathbb{C}$ is the field $\mathbb{R}$.
\end{example}

\begin{remark}
    The ground field $F$ need not always be the fixed field of the group $\gal_F K$.
\end{remark}

\begin{example}
    $\sqrt[3]{2}$ is the root of $x^3 - 2 = 0$. So $\sqrt[3]{2} \mapsto \{ \sqrt[3]{2}, \sqrt[3]{2} \omega, \sqrt[3]{2} \omega^2 \}$, 
    where $\omega$ is the cube root of unity.

    However, $\sqrt[3]{2} \omega, \sqrt[3]{2} \omega^2 \notin \mathbb{Q}[\sqrt[3]{2}]$. $\forall \sigma \in \gal_\mathbb{Q} \mathbb{Q}[\sqrt[3]{2}]$,
    $\sigma(\sqrt[3]{2}) = \sqrt[3]{2}$. Thus $\sigma = 1$. The fixed field of $\gal_\mathbb{Q} \mathbb{Q}[\sqrt[3]{2}]$ is 
    $\mathbb{Q}[\sqrt[3]{2}]$.
\end{example}

\begin{theorem}
    Suppose the extension $E/F$ is a splitting field of some polynomial. Then $\forall \alpha \in E$, 
    the minimal polynomial of $\alpha$ must split completely (into the linear factors) in $E$.
\end{theorem}
\begin{proof}
    Suppose $E$ is the splitting field of some polynomial $Q$, and we fix $\alpha \in E$ with polynomial 
    $p(x)$; then we want to show that $p(x)$ splits completely in $E$.

    Let $K$ be a subfield of $E$ where $p(x)$ splits completely. Then in $K$, we have 
    \[
        p(x) = (x - \alpha_1)(x - \alpha_2) \ldots (x - \alpha_n)
    \]
    where $\alpha_i \in K$ for all $i$ and $\alpha_1 = \alpha$. We need to check that 
    $\alpha_i \in E$ for all $i$, and we already know $\alpha \in E$.

    Again, we have that $F(\alpha_i) \cong F(\alpha)$, since $\alpha_i$ and $\alpha$ have the 
    same minimal polynomial. Now consider $E$ from the perspective of these intermediate fields. We 
    know that $E$ is the splitting field from $Q$ over $F(\alpha)$. But we do not yet know whether 
    $\alpha_i$ is in $E$ or not, but at least we know that if we adjoin it, then $E(\alpha_i)$ is 
    the splitting field for $Q$ over $F(\alpha_i)$.

    By the uniqueness of the splitting field, there exists an isomorphism $E \cong E(\alpha_i)$ extending the 
    isomorphism $F(\alpha) \cong F(\alpha_i)$. We had indentified both $F(\alpha)$ and $F(\alpha_i)$, and 
    since $Q$ has coefficients in $F$ (which preserved by the isomorphism). It is the same 
    polynomial in both fields --- the isomorphism takes one copy of $Q$ to the other. 

    Since our isomorphism is the identity of $F$, this means 
    \[
        [E:F] = [E(\alpha_i) : F],
    \]
    and since $E(\alpha_i) \supset E$, this means we must have $E(\alpha_i) = E$, and 
    therefore $\alpha_i \in E$.
\end{proof}

\subsection{Fundamental Theorem of Galois theory}

\begin{definition}[Galois correspondence]
    Let $K$ be a finite-dimensionalextension field of $F$, and let 
    $S$ be the set of all intermediate fields. Again we let 
    $T$ be the set of all subgroups of the Galois group $\gal_F K$.

    Define a map $\phi : T \to S$ by this rule. For each intermediate field $E$,
    \begin{equation}
        \phi(E) = \gal_E K.
    \end{equation} 
    This function $\phi$ is called the Galois correspondence.

    \begin{center}
        $\begin{tikzcd}
            \gal_K K \arrow[r] 
            & K \arrow[d, "S"] \\
            \gal_F K \arrow[u,"T"] \arrow[r]
            & F
            \end{tikzcd}
        $
    \end{center}
\end{definition}

\begin{example}
    \[
        \mathbb{Q} \rightarrow \gal_\mathbb{Q} \mathbb{Q}(\sqrt{3}, \sqrt{5}) = \{1, \tau, \alpha, \beta \}
    \]
\end{example}

\begin{lemma}
    Let $K$ be a finite-dimensional extension field of $F$. If $H$ is a subgroup of the Galois group 
    $\gal_F K$ and $E$ is the \bgold{fixed field} of $H$, then $K$ is 
    \textit{simple, normal, separable extension} of $E$.

    \begin{center}
        $\begin{tikzcd}
            \gal_F K  
            & K \arrow[dash]{d} \\
            H \arrow[dash]{u} \arrow[r]
            & E_H
            \end{tikzcd}
        $
    \end{center}
\end{lemma}
\begin{proof}
    Since $K$ is finite-dimensional extension field, so $K$ is algebraic over $F$. Let $\mathfrak{U} \in K$ and 
    $p(x) \in E[x]$ be minimal polynomial of $\mathfrak{U}$, and $\forall \sigma \in H$, $\sigma(\mathfrak{U})$ is 
    some root of $p(x)$.

    Therefore, $\mathfrak{U}$ has a finite number of distinct images under automorphisms in $H$, said 
    \[
        \mathfrak{U} = u_1, u_2, \ldots, u_t \in K, \quad \text{where } t \leq \deg\, p(x)
    \]
    If $\sigma \in H$ and $u_i = \tau(\mathfrak{U})$ with $\tau \in H$, then $\sigma(u_i) = \sigma \circ \tau (\mathfrak{U})$.

    Since $\sigma$ is injective, so 
    \[
        \mathfrak{U} \xhookrightarrow{H} \{ u_1, u_2, \ldots, u_t \}
    \]
    which $\{ u_1, u_2, \ldots u_t\}$ is image of $\mathfrak{U}$. And $u_i = \tau(\mathfrak{U})$ for some $\tau \in H$.
    is injective 
    \[
        \{ u_1, u_2, \ldots, u_t \} \xhookrightarrow[\text{permutation } \sigma]{} \{ u_1, u_2, \ldots, u_t \}
    \]
    Every automorphism in $H$ permutes $u_1, u_2, \ldots, u_t$. Let 
    \[
        f(x) = (x-u_1)(x-u_2)\ldots(x-u_t)
    \]
    Since all $u_i$'s are distinct, $f(x)$ is separable.

    Now we claim that $f(x) \in E[x]$. Note that $\sigma f(x) = f(x)$ for all $\sigma \in H$. All coefficients of 
    $f(x)$ is fixed by $\sigma \in H$. Thus $f(x) \in E[x]$. Since $u = u_1$ is a root of $f(x) \in E[x]$, $u$ is separable over 
    $E. \Longrightarrow \> K$ is separable extension of $E$.

    From the previous theorem, $K = E(V)$ for some $V \in K$. Let $g(x) = (x - v)(x - v_2) \ldots (x - v_s)$ 
    where $\{ v_1 = v, v_2, \ldots, v_s \}$ are images of $\sigma \in H$. Similarly, $g(x) \in E[x]$ and 
    $K = E(v)$ is splitting field of $g(x)$. Therefore $K$ is normal extension of $E$.
\end{proof}

\begin{definition}[Galois extension]
    If $K$ is a finite dimensional, normal, separable extension field of the field $F$, we say that 
    $K$ is a Galois extension of $F$ or that $K$ is Galois over $F$.
\end{definition}

\begin{corollary}
    Let $K$ be a finite dimensional extension field of $F$. Then $K$ is Galois over $F$ if and only if
    $F$ is fixed field of the Galois group over $F$.
\end{corollary}
\begin{proof}
    $(\Rightarrow)$ By previous theorem, $E = F$. Thus $F$ is fixed field of the Galois group over $F$.

    $(\Leftarrow)$ By lemma, $K$ is simple, normal, separable extension of $F$.
\end{proof}

\begin{theorem}[Fundamental theorem of Galois Theory]
    If $K$ is a Galois extension field of $F$, 
    \begin{enumerate}
        \item There is a bijection between the set $S$ of all the intermediate fields of the extension and 
            the set $T$ of all subgroups of the Galois group $\gal_F K$, given by assigning each intermediate 
            field $E$ to the subgroup $\gal_E K$. Furthermore
            \[
                |K:E| = |\gal_E K|
            \]
            and 
            \[
                |E:F| = |\gal_F K : \gal_E K|.
            \]
        
        \item An intermediate field $E$ is normal extension of $F$ if and only if the 
            corresponding group $\gal_E K$ is a normal subgroup of $\gal_F K$.
    \end{enumerate}
\end{theorem}
\begin{proof}
    \begin{enumerate}
        \item By theorem, fixed field of $\gal_E K$ is $E$. By theorem we have 
        \[
            |\gal_E K| = |K:E|.
        \]
        Similarly,
        \[
            |\gal_F K| = |K:F|.
        \]
        In fact $|K:F| = |K:E|\,|E:F|$. Thus 
        \[
            |\gal_F K| = |\gal_E K| \cdot |E:F| \Longrightarrow |E:F| = |\gal_F K: \gal_E K|. 
        \]

        \item $(\Leftarrow)$ Assume first that $\gal_E K$ is a normal subgroup of $\gal_F K$. If $p(x)$ 
        is an irreducible polynomial in $F[x]$ with a root $u \in E$, we must show that $p(x)$ splits in $E[x]$.

        Since $K$ is normal over $F$. We know that $p(x)$ splits in $K[x]$. So we know that $p(x)$ also splits 
        in $K[x]$. So we need to show that each root $v$ of $p(x)$ in $K$ is actually in $E$. There is an automorphism 
        $\sigma \in \gal_F K$ such that $\sigma(u) = v$ by theorem. So $\gal_F K = |K:F| = E$.

        \[
            \begin{tikzcd}[row sep=2.5em]
                K=F(u) \arrow[r, "\sigma"] \arrow[dash]{d} & F(u) = K \arrow[dash]{d}\\
                F \arrow[r, "1"] & F
            \end{tikzcd}
        \]

        Now if $\tau$ is any element of $\gal_E K$, then normality implies 
        \[
            \tau \circ \sigma = \sigma \circ \tau' \quad \textsf{ for some } \tau' \in \gal_E K.
        \]
        Since $u \in E$, we have 
        \begin{align*}
            \tau(v) &= \tau \left( \sigma(u) \right)\\
            &= \sigma \left( \tau'(u) \right)\\
            &= \sigma(u)\\ 
            &= v.
        \end{align*}
        So $\gal_E K$ fixes other roots for all $v \in E$. Thus $E$ is normal extension of $F$.

        $(\Rightarrow)$ Assume that $E$ is normal subgroup of $F$. Then there exists a surjective 
        homomorphism of groups $\theta: \gal_F K \to \gal_F E$ whose kernel is 
        $\gal_E K$. Then $\gal_E K$ is normal subgroup of $\gal_F K$. 

        Therefore by First isomorphism theorem, $\gal_F E \cong \gal_F K / \gal_E K$.
    \end{enumerate}
\end{proof}

\begin{lemma}
    Let $K$ be a finite-dimensional normal extension field of $F$ and $E$ an intermediate field 
    which is normal over $F$. Then there is a surjective homomorphism of groups
    \[
        \theta : \gal_F K \to \gal_F E
    \]
    where kernel of $\theta$ is $\gal_E K$.
\end{lemma}
\begin{proof}
    Let $\sigma \in \gal_F K$ and an $u \in E$. Then $u$ is algebraic over $F$ with minimal polynomial 
    $p(x)$.

    Since $E$ is normal, all roots of $p(x)$ are in $E$. Since $\sigma(u)$ is also 
    root of $p(x)$, $\sigma(u) \in E$. Therefore
    \[
        \sigma(E) \subseteq E \quad \forall \sigma \in \gal_F K.
    \]
    Thus we can restrict $\sigma$ to $E$ and $\sigma \circ 1_E$ is an $F$-isomorphism 
    that is $E \cong \sigma(E)$. Hence,
    \[
        |E:F| = |\sigma(E):F|.
    \]

    Since $K$ is splitting field over $F$, $K$ is also splitting field over $E$. $\forall \sigma \in \gal_F E$. 
    $\sigma$ can be extended to an $F$-automorphism in $\gal_F K$. Its kernel consists of the automorphisms of $K$
    whose restriction to $E$ is the identity map as $\gal_E K$.
\end{proof}

\begin{example}
    Let $K$ be the splitting field of $x^3 - 2$. Note that 
    \[
        \mathbb{Q} \subseteq \mathbb{Q}[\sqrt[3]{2}] \subseteq K
    \]
    and $|\mathbb{Q}[\sqrt[3]{2}]: \mathbb{Q}| = 3$. $K$ is Galois extension of $\mathbb{Q}$ 
    such that 
    \[
    | \gal_\mathbb{Q} K| = |K:\mathbb{Q}|
    \]
    and $\gal_\mathbb{Q} K$ is isomorphic to a subgroup of $S_3$.

    \begin{align*}
        3 < |K:\mathbb{Q}| \leq 6 &\Longrightarrow 3 < |K: \mathbb{Q}[\sqrt[3]{2}]| \cdot |\mathbb{Q}[\sqrt[3]{2}] : \mathbb{Q}| \leq 6\\
        &\Longrightarrow 3 < 3\, |K: \mathbb{Q}[\sqrt[3]{2}] | \leq 6\\
        &\Longrightarrow 1 < |K: \mathbb{Q}[\sqrt[3]{2}] | \leq 2.
    \end{align*}
    We must have $|K: \mathbb{Q}| = 6$ and $\gal_\mathbb{Q} K \cong S_3$.

    $\mathbb{Q}[\omega]$ is the splitting field of $x^2 + x + 1$ and hence $\mathbb{Q}[\omega]$ is 
    normal and separable. Thus $K$ is Galois over $\mathbb{Q}$.
\end{example}

\section{Solvability by Radicals}

We shall assume that all fields have characteristic $0$. A "formula" is a specific procedure 
that starts with coefficients of the polynomial $f(x) \in F[x]$ and arrives at the solutions of equation
$f(x) = 0_F$ by using only the field operations $(+_F, -_F, \times_F, \div_F)$ and the extraction 
of roots (such as $\sqrt[n]{\cdot}$).

In this context, an $n$-th root of an element $c$ in field $F$ is any root of the polynomial 
$x^n - c$ in some extension field of $F$. If that "formula" really exists, then there exists 
an extension field $K$ of $F$ such that 
\[
    \begin{tikzcd}
        F \arrow[rr, blue, bend left=50, "\text{splitting field of } x^n - c"] & \supseteq & F' \arrow[rr, red, bend left=50, "\text{splitting field of } x^{n'} - c'"] & \supseteq & \ldots \arrow[rr, bend left=50]& \supseteq & K\\
    \end{tikzcd}
\]

\begin{definition}[Radical extensions]
    A field $K$ is said to be a radical extension of a field $F$ if there is a chain of fields 
    \[
        F = F_0 \subseteq F_1 \subseteq \ldots \subseteq F_t = K
    \]
    such that for each $i = 1, 2, \ldots, t$. $F_i = F_{i - 1}(u_i)$ and 
    some power of $u_i$ is in $F_{i-1}$ ($u_i^{k_{i}} \in F_{i-1}$). 
    
    The equation $f(x) = 0_F$ is said to be solvable by radicals if there is a radical extension of $F$ that contains 
    a splitting field of $f(x)$.
    If not, then $f(x)$ is not solvable by radical.
\end{definition}

Think of this, said $K$ is a radical extension of a field $F$ if there exist nonzero elements 
$u_1, u_2, \ldots, u_m \in K$ and positive integers $n_1, n_2, \ldots, n_m$ such that $K = F(u_1, u_2, \ldots, u_m)$, and 
\begin{align*}
    u^{n_1}_1 &\in F,\\
    u^{n_2}_2 &\in F(u_1),\\
    u^{n_3}_3 &\in F(u_1, u_2),\\
    &\vdots\\
    u^{n_k}_k &\in F(u_1, u_2, \ldots, u_{k-1}).\\
\end{align*}
The definition expresses that $u_i$ is an $n_i$-th root of some element in $F(u_1, u_2, \ldots, u_{i-1})$, so $K$ may be 
thought of as being built by iteratively adding in $n$-th roots of elements. The picture depicted 
as following:

\newpage 
\begin{center}
    $\begin{tikzcd}
        K = F(u_1, u_2, \ldots, u_m) \arrow[dash]{d} \\
        u^{n_m}_m \in F(u_1, u_2, \ldots, u_{m-1}) \arrow[dash]{d}\\
        \vdots \arrow[dash]{d}\\
        u^{n_2}_2 \in F(u_1) \arrow[dash]{d}\\
        u^{n_1}_1 \in F
        \end{tikzcd}
    $
\end{center}

\begin{example}
    Show that the field $\mathbb{Q}\left( \sqrt{3 + \sqrt{21}}\right)$ has degree 
    4 over $\mathbb{Q}$ and hence find a basis.
\end{example}
\begin{solution}
    We let $\alpha = \sqrt{3 + \sqrt{21}}$, and 
    \[\alpha^2 = 3 + \sqrt{21} \implies \alpha^2 - 3 = \sqrt{21}. \]
    Squaring both sides gives 
    \[
        (\alpha^2 - 3)^2 = 21 \implies x^4 - 6x^2 -12 = 0
    \]
    However, the polynomial $q(x) = x^4 - 6x^2 -12$ is irreducible over $\mathbb{Q}$ by Eisenstein's 
    criterion with $p=3$. Thus, $q(x)$ must be the minimal polynomial of $\alpha$. 

    Therefore, by results, we see that $[\mathbb{Q}:\mathbb{Q}(\alpha)]$ and that the basis is 
    $\{1, \alpha, \alpha^2, \alpha^3 \}$.
\end{solution}

\begin{example}
    The solutions of $x^3 + 3x + 2 = 0 \in \mathbb{Q}[x]$ are 
    \[
    \fbox{$\sqrt[3]{-1+\sqrt{2}} + \sqrt[3]{-1-\sqrt{2}}$} \quad \fbox{$\omega \sqrt[3]{-1+\sqrt{2}} + (\omega^2) \sqrt[3]{-1-\sqrt{2}}$}
    \quad \fbox{$(\omega^2) \sqrt[3]{-1+\sqrt{2}} + \omega \sqrt[3]{-1-\sqrt{2}}$}
    \]
\end{example}

\begin{definition}[Solvable groups]
    A group $G$ is said to be solvable if it has a "chain" of subgroups 
    \[
        G = G_0 \triangleright G_1 \triangleright \ldots \triangleright G_{n-1} \triangleright G_n 
        = \langle e \rangle
    \]
    and $G_{i-1} / G_i$ is abelian.
\end{definition}

\begin{example}
    Every abelian group $G$ is solvable. $G \supseteq \langle e \rangle$ and $G/\langle e \rangle \cong G$ 
    is abelian.
\end{example}
\begin{solution}
    Since $S_3 \triangleright \langle (1\, 2\, 3) \rangle$, and 
    \[
        (1\, 2) \, \langle (1\, 2\, 3) \rangle = \{ (1 \, 2), (1 \, 3), (2\, 3)\}
    \]
    \[
        \langle (1\, 2\, 3) \rangle\, (1\, 2) = \{ (1 \, 2), (2 \, 3), (1\, 3)\}
    \]
\end{solution}

\begin{theorem}
    Let $K$ be a field extension of $F$. If $\text{char } K \nmid n$ and $K$ contains a 
    primitive $n$-th root of unity, then
    \begin{enumerate}
        \item For $a \in K$, let $F = K(\sqrt[n]{a})$. The extension $F/K$ is cyclic 
        of degree $d$, a divisor of $n$.
        \item Conversely, if $F/K$ is a cyclic extension of degree $n$, then 
        $F = K(\sqrt[n]{a})$ for some $a \in K$.
    \end{enumerate}
\end{theorem}
\begin{proof}
    \begin{enumerate}
        \item The statement hold trivially when $a = 0$. So we further assume that $a \neq 0$. Because 
        $K \subset F$ contains a primitive $n$-th root of unity, $F$ is the splitting field of 
        $x^n - a$ over $K$. Since $\text{char } K \nmid n$, there are $n$ distinct $n$-th roots of unity,
        so the polynomial $x^n - a$ must have $n$ number of roots $\sqrt[n]{a} \xi^i$ for all 
        $i = 0, 1, \ldots, n-1$, where $\xi$ is a primitive $n$-th root of unity in $K$.
        Therefore $x^n - a$ is separable and $F/K$ is Galois extension.

        Consider each $\sigma$ in $\gal_FK$ is completely determined by $\sigma(\sqrt[n]{a})$, which must 
        equal to $\sqrt[n]{a} \xi^{i_\sigma}$. Consider the map 
        \[
            \gal_FK \to \mathbb{Z}_n
        \]
        \[
            \sigma \mapsto i_\sigma
        \]
        Clearly, this map is injective homomorphism, and it is easy to check
        \[ 
            \tau \sigma (\sqrt[n]{a}) = \tau(\sqrt[n]{a} \xi^{i_\sigma}) = \sqrt[n]{a} \xi^{i_\sigma} \xi^{i_\tau} = \sqrt[n]{a} \xi^{i_\sigma + i_\tau}.
        \]

        \item Let $\gal_FK = \langle \sigma \rangle$ be cyclic group of order $n$. For 
        $\alpha \in F$ and $\xi$ a primitive $n$-th root of unity, define the 
        \textit{Lagrange resolvent} by 
        \[
            P(\alpha, \xi) := \alpha + \xi \sigma(\alpha) + \xi^2 \sigma^2(\alpha) + \ldots + \xi^{n-1} \sigma^{n-1}(\alpha).
        \]
        By corollary, $\{1, \sigma, \sigma^2, \ldots, \sigma^{n-1}\}$ are linearly independent over $F$.
        So we have
        \begin{equation}
            1 + \xi \sigma + \xi^2\sigma^2 + \cdots + \xi^{n-1} \sigma^{n-1} \neq 0
        \end{equation}
        so there is $\alpha \in F$ such that $P(\alpha, \xi) \neq 0$. Now let $\rho := P(\alpha, \xi)$.
        Since $\xi \in K$, we have $\sigma(\rho) = \xi^{-1} \rho$, and that 
        \[
            \sigma(\rho^n) = \xi^{-n} \rho^N = \rho^n.
        \]
        So $\rho^n \in F_{\langle \sigma \rangle} = K$. Moreover, 
        \[
            \sigma^i(\rho) = \xi^{-i} \rho \neq \rho \quad \forall i = 0, 1, \ldots, n-1.
        \]
        Thus $\sigma^i \notin \aut_{K(\rho)} F$. i.e. $|\aut_{K(\rho)} F| = 1$. Therefore it deduce to 
        \[
            F = K(\rho) = K(\sqrt[n]{a}),
        \]
        where $a = \rho^n \in K$.

        \begin{center}
        $\begin{tikzcd}
        F \arrow[dash]{d} \\
        K(\rho) \arrow[dash]{d}\\
        K \\
        \end{tikzcd}
        $   
        \end{center}
        
    \end{enumerate}
\end{proof}

\begin{theorem}
    For $n \geq 5$ the group $S_n$ is not solvable.
\end{theorem}
\begin{proof}
    For the sake of contradiction, suppose that 
    $S_n$ is solvable and that 
    \[
        S_n = G_0 \supseteq G_1 \supseteq \cdots \supseteq G_t = \langle 1 \rangle.
    \] 
    Let $(r\, s\, t)$ be any 3-cycle in $S_n$ and let $\alpha, \beta$ be any 
    element of $\{1, 2, \ldots, n\}$ other than $r, s, t$ (they always exist since $n \geq 5$).
    Since $S_n / G_1$ is abelian, by theorem of dihedral group,
    \begin{align*}
        (t\, \alpha\, s)(s\, r\, \beta)(t\, \alpha\, s)^{-1} (s\, r\, \beta)^{-1} &= 
        (t\, \alpha\, s)(s\, r\, \beta)(t\, s\, \alpha)(s\, \beta\, r)\\
        &= (r\, s\, t) \in G_1
    \end{align*}
    Note that the cycle $\langle (r\, s\, t) \rangle \subseteq G_1$, and $G_1$ definitely contains all the 3-cycles 
    since $G_1/G_2$ is abelian, repeating upper process, $G_2$ also contains $\langle (r\, s\, t) \rangle$.
    
    In conclusion, $\forall i \in \{1,2,\ldots, n\}$, $G_i$ contains all the 3-cycles. This contradicting the fact 
    that $S_n$ is solvable.
\end{proof}

\begin{theorem}
    Every homomorphic image of a solvable group $G$ is solvable.
\end{theorem}
\begin{proof}
    Let $G$ be a solvable group. Then there exists a chain of groups 
    \[
        G = G_0 \supseteq G_1 \ldots \supseteq G_n = \langle e \rangle
    \]
    such that for all $i$, $G_{i-1} \triangleright G_i$ and $G_{i-1}/G_i$ is abelian.

    Consider $f$ is the homomorphism of $G$. Then $f(G_i)$ is also a group, and the chain of group is now 
    \[
        f(G) = f(G_0) \supseteq f(G_1) \ldots \supseteq f(G_n) = \langle e \rangle
    \]
    and $aba^{-1}b^{-1} \in G_i$ whenever $a,b$ in $G_{i-1}$. This implies 
    \[
        f(aba^{-1}b^{-1}) = f(a)f(b) f(a)^{-1}f(b)^{-1} \in f(G_i) \quad \forall a,b \in G_{i-1}
    \]
    and 
    \[
        \forall c, d \in f(G_{i-1}), \exists a,b \in G_{i-1} \quad s.t. \> f(a) = c \textsf{ and } f(b) =d.
    \]
    So we have 
    \[
        f(a)f(b) f(a)^{-1}f(b)^{-1} = cdc^{-1}d^{-1} \in f(G_i).
    \]
    Therefore $f(G_{i-1})/f(G_i)$ is abelian. Hence $f(G)$ is solvable group.
\end{proof}

\begin{definition}
    A generator of this cyclic group of $n$-th roots of unity in $K$ is called a primitive $n$-th root of unity.
\end{definition}

This definition states that $\zeta$ is a primitive $n$-th roots of unity iff $\zeta, \zeta^2, \ldots, \zeta^n$ 
are the $n$ distinct $n$-th roots of unity.

\begin{example}
    Consider $x^4 - 1 \in \mathbb{Q}[x]$. The 4-th roots of unity in $\mathbb{C} = \{1, -1, i, -1\} = \langle i \rangle$.
    $i$ and $-i$ are primitive 4-th root of unity in $\mathbb{C}$.
\end{example}

\begin{example}
    According to De Moivre's theorem,
    \[
        \cos \left(\frac{2 \pi}{n}\right) + i \sin \left(\frac{2 \pi}{n}\right)
    \]
    is a primitive $n$-th root of unity in $\mathbb{C}$.
\end{example}

\begin{theorem}
    Every homomorphic image of a solvable group $G$ is solvable.
\end{theorem}
\begin{proof}
    Let $G$ be a solvable group. Then there exists a chain of groups
    \[
        G = G_0 \supseteq G_1 \supseteq \ldots \supseteq G_n = \langle  e \rangle
    \]
    such that $G_{i-1} \triangleright G_i$ and $G_{i-1} / G_i$ is abelian $\forall i$.

    Let $f$ be the homomorphism of $G$, then $f(G_i)$ is also a group. The chain of group is now 
    \[
        f(G) = f(G_0) \supseteq f(G_1) \supseteq \ldots \supseteq f(G_n) = \langle  e \rangle
    \]
    and $\forall a, b \in G_{i-1}$, we have $aba^{-1}b^{-1} \in G_i$. And 
    \[
        f(aba^{-1}b^{-1}) = f(a)f(b)f(a)^{-1}f(b)^{-1} \in f(G_i).
    \]
    And for all $c, d$ in $f(G_i)$, there exists some $a, b \in G_i$ such that $f(a) = c$ and 
    $f(b) = d$. So 
    \[
        f(a)f(b)f(a)^{-1}f(b)^{-1} = cdc^{-1}d^{-1} \in f(G_i).
    \]
    Thus $f(G_{i-1})/f(G_i)$ is abelian. Thus $f(G)$ is solvable group.
\end{proof}

\begin{lemma}
    Let $F$ be a field and $\zeta$ a primitive $n$-th root of unity of $F$. Then $F$ contains a primity $d$-th root of unity 
    for every positive divisor $d$ of $n$.
\end{lemma}
\begin{proof}
    Because $\zeta$ is a primitive $n$-th root of unity of $F$, that is, $\zeta^n = 1_F$. If $\zeta$ 
    has order $n$ and $n = dk$, $\zeta^k$ has order $d$.

    Note that $\{ \zeta^k, \zeta^{2k}, \ldots, \zeta^{nk} \}$ are all distinct and roots of $x^d - 1_F$. Thus 
    $\zeta^k$ is a primitive $d$-th root of unity.
\end{proof}

\begin{example}
    There is no formula (involving only field operations and extraction of roots) for the 
    solution of all 5th-degree polynomial equations.
\end{example}
\begin{solution}
    Consider $f(x) = 2x^5 - 10x + 5 \in \mathbb{Q}[x]$. We check the zeros of the derivatives.
    \[
        f'(x) = \odv{}{x} (2x^5 - 10x + 5) = 10x^4 - 10 \quad \Longrightarrow \textsf{roots are } \pm 1, \pm i
    \]
    \[
        f''(x) = \odv[order=2]{}{x} (2x^5 - 10x + 5) = 40x^3 \quad \Longrightarrow \textsf{the only root is } 0.
    \]

    \begin{figure}[ht]
        \pgfplotsset{compat=1.16}
        \begin{center}
            \begin{tikzpicture}
                \begin{axis}[xmin=-2, xmax=2, ymin=-15, ymax=19, axis x line=middle, axis y line=middle, legend pos=outer north east]
                \addplot[domain=-2:2, color=red, samples=200, line width=0.75pt]{2*x^5-10*x+5};
                %\node[left,red] at (1.65,15) {$2x^5-10x+5$}; 
                \legend{\(2x^5 - 10x +5\)};
                \addplot[color=red, mark=*] coordinates {(-1.601,0)};
                \addplot[color=red, mark=*] coordinates {(1.329,0)};
                \addplot[color=red, mark=*] coordinates {(0.507,0)};
                \end{axis}
            \end{tikzpicture}
        \end{center}
        \caption{By graph, $f(x) = 2x^5 - 10x + 5$ has 3 real roots.}
    \end{figure}

    Note that by Eisenstein's criterion, $5|10$, $5|4$, but $5 \nmid 2$ and $5^2 \nmid 5$. So $f(x)$ 
    is irreducible in $\mathbb{Q}[x]$. 

    If $K$ is splitting field of $f(x)$ in $\mathbb{C}$. Then 
    \[
    |\gal_\mathbb{Q} K| = [K:\mathbb{Q}]
    \]
    Since $K$ is Galois field of $\mathbb{Q}$.

    If $r$ is any root of $f(x)$, then 
    \[
        [K:\mathbb{Q}] = [K: \mathbb{Q}(r)] \cdot [\mathbb{Q}(r) : \mathbb{Q}] = 5\, [K: \mathbb{Q}(r)].
    \]
    Thus $|K : \mathbb{Q}|$ is divisible by $5$. By Cauchy's theorem, there exists $sigma \in \gal_\mathbb{Q} K$ with 
    $\ord(\sigma) = 5$. Note that $\gal_\mathbb{Q} K \subseteq S_5$ and the only elements of order 
    $5$ are (5-cycles), the 5-cycle is in $\gal_\mathbb{Q} K$. The complex conjugation $a + bi \mapsto a -bi$ 
    induces an automorphism on $K$ since $\sigma \in \gal_\mathbb{Q} \mathbb{C}, \sigma \vert_K \in \gal_\mathbb{Q} K$.
    
    Since $\sigma \vert_K$ interchanges the two nonreal roots of $f(x)$, implies that 
    $\gal_{\mathbb{Q}} K$ contains a transposition (2-cyle). Note that the only 
    subgroup of $S_5$ that contains both a 5-cycle and a transposition is $S_5$ itself.
    So $\gal_\mathbb{Q} K = S_5 \Longrightarrow f(x)$ is not solvable by radicals. 

\end{solution}

\section*{Tutorials}

\begin{mdframed}
    \vspace{-0.25cm}
    \hspace{-0.25cm}
    \begin{Exercise}
        Let $F$ be a field and $F^*$ be its multiplication group. Show that the abelian groups 
        $(F,+)$ and $(F^*, \cdot)$ are not isomorphic.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $F$ be a finite field. Show that the product of all the nonzero elements of $F$ is $-1$.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Show that any two finite fields of the same order are isomorphic.
    \end{Exercise}
    \begin{Answer}
        \textbf{[Claim]: }Any finite field $F$ with $p^n$ elements is a splitting field of 
        $x^{p^n} - x$ over $\mathbb{F}_p[x]$.

        Let $F$ be a finite field with $p^n$ elements. Consider $F \setminus \{0\}$, the 
        set of all nonzero elements of $F$. Since $F$ is a finite field, $F \setminus \{0\}$ form 
        a multiplicative group of order $p^n - 1$. It follows that 
        $F$ coincides with the set of roots of the polynomial $x^{p^n} - x$. Hence, $F$ is the splitting field of 
        $x^{p^n} - x \in \mathbb{F}_p[x]$. This completes the proof of our claim.

        Consequently, any two finite fields with $p^n$ number of elements are isomorphic. This 
        is exactly what we wanted to show.

        Let $E$ and $F$ be two finite fields with $p^n$ number of elements. By theorem 
        $E$ and $F$ must contain subfields $E_p$ and $F_p$, each also have $p$ elements. 
        Hence $E$ and $F$ are splitting fields of $x^{p^n} - x$ over $E_p$ and $F_p$, respectively.
        Again, we have 
        \[
            E_p \cong \mathbb{Z}/\langle p \rangle, \text{ and }
            F_p \cong \mathbb{Z}/\langle p \rangle 
            \implies E_p \cong F_p.
        \]
        Hence, by uniqueness of splitting fields (up to isomorphism), it follows that 
        $E$ isomorphic to $F$. This completes the proof.
    \end{Answer}

    \vspace{0.752cm}
    \begin{Exercise}
        \begin{enumerate}
            \item Prove that a finite integral domain is a field.
            \item Prove that if $R$ is an integral domain that is finite dimensional over a subfield 
            $F \subseteq R$, then $R$ is a field.
        \end{enumerate}
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $F$ be a field extension of the rational numbers.
        \begin{enumerate}
            \item Show that $\{a+b\sqrt{2} \> | \> a, b \in F \}$ is a field.
            \item Give necessary and sufficient conditions for $\{a+b\sqrt[3]{2} \> | \> a, b \in F \}$ 
                to be a field.
        \end{enumerate}
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let 
        \[
            f(x) = a_nx^n + \cdots + a_1x + a_0 \in \mathbb{Q}[x]
        \]
        be an irreducible polynomial of degree greater than 1, in which all roots lie on the unit circle of 
        $\mathbb{C}$. Show that $a_i = a_{n-i}$ for all $i$.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Find the minimal polynomial of $\alpha = \sqrt{3 + 2\sqrt{2}}$ over the field $\mathbb{Q}$ of rational numbers.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Find the minimal polynomial of $\alpha = \sqrt[3]{2 + \sqrt{2}}$ over the field $\mathbb{Q}$ of rational numbers.
    \end{Exercise}
    \begin{Answer}
        Let $\alpha = \sqrt[3]{2 + \sqrt{2}}$. Then 
        \[
            \alpha^3 = 2 + \sqrt{2} \implies (\alpha^3 - 2)^2 = 2 \implies \alpha^6 - 4\alpha^3 + 2 = 0.
        \]
        So the minimal polynomial is $f(x) = x^6 - 4x^3 + 2$ over $\mathbb{Q}$ that has $\alpha$ as a root.
    \end{Answer}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $p$ be a prime, and $f(x) \in \mathbb{Z}_p[x]$ be irreducible polynomial of degree $m$. Show that 
        $f(x) | (x^{p^n} - x)$ if and only if $m | n$. 
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $p$ and $q$ be distinct primes. Show that $\sqrt{q}$ is not an element of $\mathbb{Q}(\sqrt{p})$. 
    \end{Exercise}
    \begin{Answer}
        We proof by contradiction. Suppose not, suppose that $\sqrt{q}$ is an element of $\mathbb{Q}(\sqrt{p})$. Then 
        $\mathbb{Q}(\sqrt{p})$ is the smallest subfield containing $\mathbb{Q}$ and $\sqrt{q}$. Notice that 
        every element can be expressed as $a+b\sqrt{p}$ where $a, b \in \mathbb{Q}$. So now we let 
        \[
            \sqrt{q} = a+b\sqrt{p}. \label{eq:fs.0} \tag{{\color{orange} $\heartsuit$}}
        \]
        Now squaring both sides:
        \begin{align*}
            q = (a + b\sqrt{p})^2 &\implies q = a^2 + 2ab\sqrt{p} + b^2p\\
            &\implies  2ab\sqrt{p}  = q - a^2 - b^2p. \label{eq:fs.1} \tag{{\color{myred} $\clubsuit$}}
        \end{align*}
        Now consider three possible cases:

        \textbf{Case 1}: If $2ab \neq 0$, then from \eqref{eq:fs.1} we express $\sqrt{p}$ in term of $p, q, a, b$:
        \[
            \sqrt{p} = \frac{q - a^2 - b^2p}{2ab}
        \]
        and $\sqrt{p}$ is rational and this contradicts 
        the fact that $p$ is prime. 

        \textbf{Case 2}: If $a = 0$, then \eqref{eq:fs.0} becomes $\sqrt{q} = b\sqrt{p}$. Squaring both sides 
        gives $q = b^2p$, so 
        \[
            \frac{q}{p} = b^2, \text{ where } b \in \mathbb{Q}.
        \]
        Because $b$ is rational, so is $b^2$. However, $\frac{q}{p}$ should be the ratio 
        of distinct primes, which is not a perfect square of a rational. Again, this 
        is a contradiction.

        \textbf{Case 3}: If $b = 0$, then \eqref{eq:fs.0} becomes $\sqrt{q} = a \implies q = a^2$. 
        Since $q$ is prime, it cannot be the square of rational numbers (Unless $a = 0$, but 
        $q$ is prime. So $q$ always greater than zero). And if $a$ is rational, $a^2 = q$ 
        and $a = \pm \sqrt{q}$, which is absurd.

        In conclusion, with all these cases, we said that 
        $\sqrt{q} \notin \mathbb{Q}(\sqrt{p})$ if $p$ and $q$ are coprime. This completes the proof.
    \end{Answer}

    \vspace{0.752cm}
    \begin{Exercise}
        Determine the Galois group of $x^4 - 3$ over the field $\mathbb{Q}$.
    \end{Exercise}
    \begin{Answer}
        The roots of polynomial $p(x) = x^4 - 3$ are 
        \[
            \alpha_1 = \sqrt[4]{3},\quad \alpha_2 = -\sqrt[4]{3},\quad
            \alpha_3 = i\sqrt[4]{3},\quad \alpha_4 = -i\sqrt[4]{3}.
        \]
        The splitting field $K$ that generated by all the roots over $\mathbb{Q}$ is 
        $K = \mathbb{Q}(\sqrt[4]{3}, i)$. Now we need to determine the degree of field 
        extension $[K : \mathbb{Q}]$. 

        \begin{center}
        $\begin{tikzcd}
        \mathbb{Q}(\sqrt[4]{3}, i) \arrow[dash]{d} \\
        \mathbb{Q}(\sqrt[4]{3}) \arrow[dash]{d}\\
        \mathbb{Q} \\
        \end{tikzcd}
        $   
        \end{center}

        The polynomial $x^4 - 3$ is irreducible 
        over $\mathbb{Q}$ by Eisenstein's criterion with $p=3$, and $[\mathbb{Q}(\sqrt[4]{3}) : \mathbb{Q}] = 4$. 
        and the imaginary unit $i$ is not in the subfield $\mathbb{Q}(\sqrt[4]{3})$, 
        so 
        \[
             [\mathbb{Q}(\sqrt[4]{3}): \mathbb{Q}] = 2.
        \]
        The total degree of the field extension is
        \begin{align*}
            [K:\mathbb{Q}] &= [\mathbb{Q}(\sqrt[4]{3}, i) : \mathbb{Q}(\sqrt[4]{3})] \times [\mathbb{Q}(\sqrt[4]{3}): \mathbb{Q}]\\
            &= 2 \times 4\\
            &= 8
        \end{align*}
        The degree of field extension is equal to the order of galois group $\gal_{\mathbb{Q}} K$. So the order of 
        $\gal_{\mathbb{Q}} K$ is also $8$.

        The automorphisms of the galois group $\gal_{\mathbb{Q}} K$ is generated by $\sqrt[4]{3}$ 
        and $i$. We can define two automorphisms:
        \[
            \sigma : \sigma(\sqrt[4]{3}) = i\sqrt[4]{3}, \quad \sigma(i) = i;
        \]
        \[
            \rho : \rho(\sqrt[4]{3}) = \sqrt[4]{3}, \quad \rho(i) = -i;
        \]
        Now, notice that these automorphisms satisfies $\sigma^4 = 1$, $\rho^2 = 1$, and 
        $\rho \sigma \rho^{-1} = \sigma^3$. This is isomorphic to dihedral group of order $8$, $D_8$.
        Thus $\gal_{\mathbb{Q}} K \cong D_8$.
    \end{Answer}

    \vspace{0.752cm}
    \begin{Exercise}
        Determine the Galois group of $x^3 + 3x^2 - 1$ over the field $\mathbb{Q}$.
        
        [Hint]: The discriminant for general cubic equation $ax^3 + bx^2 + cx + d = 0$ is 
        \[
            \Delta = b^2 c^2 - 4ac^3 - 4b^3d - 27 a^2 d^2 + 18abcd.
        \]
    \end{Exercise}
    \begin{Answer}
        First off, we perform a basic calculus --- find the derivative of polynomial $f(x) = x^3 + 3x^2 - 1$.
        The derivative of $f$ is 
        \[
            f'(x) = 3x^2 + 6x, \quad \implies \text{roots are } -2, 0.
        \]
        Check that $f(-3) = -1 < 0$; $f(-1) = 1 > 0$; $f(1) = 3 > 0$. There is one root in $\mathbb{R}$, 
        two roots in $\mathbb{C}$. Since there are no rational roots, $f$ is irreducible over $\mathbb{Q}$.

        The galois group of irreducible cubic polynomial is either $A_3$ or $S_3$ --- we want determine which is it.
        If the discriminant of an irreducible cubic is a perfect square in $\mathbb{Q}$, then the galois group 
        is cyclic with order 3 and hence isomorphic to $A_3$. Otherwise the galois group is $S_3$.

        Check the discriminant for $f(x) = x^3 + 3x^2 - 1$:
        \[
            \Delta = (3^2 * 0^2) - 4(1)(0)^3 - 4(3^3)(-1) - 27(-1)^2 + 18 (1 * 3 * 0 * -1) = 81.
        \]
        Since $\Delta = \sqrt{81} = 9 \in \mathbb{Q}$, so the galois group of 
        $x^3 + 3x^2 - 1$ over $\mathbb{Q}$ is $A_3$.
    \end{Answer}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $f(x) = x^4 + x^3 + 4x - 1 \in \mathbb{Z}_5[x]$. Find the Galois group of the 
        splitting field of $f$ over $\mathbb{Z}_5$.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $K$ be a Galois extension of the field $F$ with Galois group $G$. Let $g(x)$ be a monic polynomial
        over $F$ that splits over $K$ (that is, $K$ contains a splitting field for $g(x)$ over $F$) and let 
        $\Gamma \subseteq K$ be the set of roots of $g(x)$. Show that $g(x)$ is a power of a polynomial 
        that is irreducible over $F$ if and only if $G$ is transitive on $\Gamma$.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $f(x) \in \mathbb{Q}[x]$ be an irreducible polynomial of degree 4 with exactly two real roots.
        Show that the Galois group of $f$ over $\mathbb{Q}$ is either $S_4$ or the 
        dihedral group of order 8.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Show that the multiplicative group of a finite field must be cyclic.
    \end{Exercise}
    \begin{Answer}
    Let $F$ be a finite field with $|F| = q$. Consider the multiplicative group $F^* = F \setminus \{0_F\}$.
    So $|F^*| = q - 1$. We want to show that there exists an element $a \in F^*$ such that 
    $\ord(a) = q - 1$. We will appeal to a property of finite abelian groups: the order 
    of every element in a finite abelian group divides the maximum order of all the elements.

    Let $m$ be the maximum order of all the elements in $F^*$. Since the order of every element 
    in $F^*$ divides $m$, each $a \in F^*$ satisfies $a^m = 1_F$. Thus, every element of $F^*$ is a root of 
    the polynomial $x^m - 1_F$. Since $x^m - 1_F$ has at most $m$ roots in $F$, we have $q - 1 \leq m$.
    At the same time, by Lagrange's theorem, $m$ divides $q - 1$. Thus $m = q - 1$.
    Hence, this implies that there exists an element $a \in F^*$ such that $\ord(a) = q - 1 = |F^*|$. 
    Therefore, $F^*$ is cyclic.
    \end{Answer}

    \vspace{0.752cm}
    \begin{Exercise}
        Show that every finite extension of a finite field is a Galois extension.
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $E$ be an extension field of a field $F$ and let $\alpha \in E$ be transcendental over $F$. Show that every element of $F(\alpha)$ is not in $F$ 
        is also transcendental over $F$. 
    \end{Exercise}

    \vspace{0.752cm}
    \begin{Exercise}
        Let $F$ be a finite field of characteristic $p$. Show that every element of $F$ is algebraic over the 
    prime field $\mathbb{Z}_p \leq F$.
    \end{Exercise}
\end{mdframed}

\newpage\null\thispagestyle{blank}\newpage